Who introduced the bug? The importance of the previous commit

### 2016-01-27 paperMSR.tex
Added data from OpenStack

\section{Related Work}
\label{sec:related}
First SZZ, the first algorithm to identifying bug-introducing code changes automatically was described in \cite{sliwerski2005changes}. Currently, is a well-known algorithm called SZZ, which is based on text diferencing to discover modified, added and delete lines between the bug-fix and its previous version. SZZ uses CVS annotate command to identify the last commit that touched these lines.

Second, a improvement on SZZ algorithm is described in \cite{kim2006automatic}, the authors used annotation graphs instead of CVS annotation to locate, in previous versions, the affected lines by modification and deletion. Also, they deleting some false positives as blank spaces, changes in the format or changes in the comments.
Then SZZ revisited\\

Then Buginnings \cite{sinha2010buginnings} is not a text-based technique as SZZ, the authors analized the effects of bug-fix changes on program dependences. Taking into account the semantic of the source code they achieved more accuracy identifying the origins of a bug.

@@

Finally our idea.

@@

OpenStack is composed by 10 projects, but we only focused in the four more actives in the 2015, Nova, Cinder, Neutron and Horizon as we can see in table \ref{tab:OpenStack}
\begin{table}[htb]
\centering
%\begin{center} {\footnotesize
\caption{ Commits per Project in OpenStack}
\label{tab:OpenStack}
\begin{tabular}{lll}
\toprule[0.3mm]%{\smallskip}
  & All History \kern 1pc & Last Year (2015) \\\hline
Nova    \kern 1pc & - & - \\
Fuel    \kern 1pc & - & -  \\
Netron  \kern 1pc & - & - \\
Openstack-manuals \kern 1pc & - & -  \\
Horizon \kern 1pc & - & -  \\
Cinder  \kern 1pc & - & - \\
Keystone\kern 1pc & - & -  \\
Heat    \kern 1pc & - & -  \\
Glance  \kern 1pc & - & - \\
Tempest \kern 1pc & - & - \\
\bottomrule[0.3mm]
\end{tabular} %}
%\end{center}
\end{table}

>>>>

\section{Related Work}
\label{sec:related}
The first algorithm to identifying bug-introducing code changes automatically was described in \cite{sliwerski2005changes}. Currently, is a well-known algorithm called SZZ, which is based on text diferencing to discover modified, added and delete lines between the bug-fix and its previous version. SZZ uses CVS annotate command to identify the last commit that touched these lines.

An improvement on SZZ algorithm is described in \cite{kim2006automatic}, the authors used annotation graphs instead of CVS annotation to locate, in previous versions, the affected lines by modification and deletion. Also, they deleting some false positives as blank spaces, changes in the format or changes in the comments.

Other methodology to identify the origins of a bug is describes in \cite{sinha2010buginnings}, this work doesn't present a text-based technique as SZZ, the authors analized the effects of bug-fix changes on program dependences. Taking into account the semantic of the source code they achieved more accuracy identifying the origins of a bug.

@@

Exists several articles based on SZZ such as \cite{williams2008szz} revisied SZZ algorithm, tracking bug-inducing changes and identify change types of them. Also, in \cite{yangbug} the authors applyed this algorithm to find out what kind of bug-inducing changes are likely to become in a great threat after being marked as bug-fix changes.In addition, new techniques in bug prediction are based in this algotimh such as \cite{kim2008classifying} which was the first work classifying file changes as buggy or clean using change information features and source code terms.

In addition some tools are based on SZZ too such as \cite{} 
Finally our idea.

@@

OpenStack is composed by 9 projects, but we only focused in the four of them, Nova, Cinder, Neutron and Horizon as we can see in table \ref{tab:OpenStack} these projects are really actives during all their history and in the last year.
\begin{table}[htb]
\centering
%\begin{center} {\footnotesize
\caption{ Commits per Project in OpenStack}
\label{tab:OpenStack}
\begin{tabular}{lll}
\toprule[0.3mm]%{\smallskip}
  & All History \kern 1pc & Last Year (2015) \\\hline
Nova    \kern 1pc & 14,558 & 3,283 \\
Fuel    \kern 1pc & 9,139 & 5,123 \\
Netron  \kern 1pc & 8,452 & 3,855 \\
Horizon \kern 1pc & 4,871 & 1,994 \\
Cinder  \kern 1pc & 4,556 & 1,832 \\
Keystone\kern 1pc & 4,874 & 1,795  \\
Heat    \kern 1pc & 6,395 & 2,372  \\
Glance  \kern 1pc & 2,651 & 723 \\
Tempest \kern 1pc & 4,141 & 1,312 \\
\bottomrule[0.3mm]
\end{tabular} %}
%\end{center}
\end{table}
